\documentclass[12pt,a4paper]{article}

% --- Packages ---
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{float}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{multirow}
\usepackage{tabularx}

% --- Colors ---
\definecolor{codeblue}{rgb}{0.16,0.32,0.75}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codegreen}{rgb}{0.0,0.5,0.0}
\definecolor{codebg}{rgb}{0.97,0.97,0.97}
\definecolor{iitgnblue}{rgb}{0.12,0.29,0.53}

% --- Listings style ---
\lstset{
  basicstyle=\ttfamily\footnotesize,
  backgroundcolor=\color{codebg},
  keywordstyle=\color{codeblue}\bfseries,
  commentstyle=\color{codegreen},
  stringstyle=\color{red!70!black},
  numbers=left,
  numberstyle=\tiny\color{codegray},
  numbersep=8pt,
  breaklines=true,
  frame=single,
  rulecolor=\color{codegray!40},
  tabsize=4,
  showstringspaces=false,
  captionpos=b,
}

\lstdefinestyle{python}{language=Python, morekeywords={self,True,False,None,as,with}}

% --- Header/Footer ---
\setlength{\headheight}{14.5pt}
\addtolength{\topmargin}{-2.5pt}
\pagestyle{fancy}
\fancyhf{}
\rhead{CS 432: Databases}
\lhead{Assignment 3 Report}
\cfoot{\thepage}

% --- Title formatting ---
\titleformat{\section}{\Large\bfseries\color{iitgnblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries\color{iitgnblue!80}}{}{0em}{}

\hypersetup{
  colorlinks=true,
  linkcolor=iitgnblue,
  urlcolor=codeblue,
  citecolor=codeblue,
}

% =====================================================================
\begin{document}

% --- Title Page ---
\begin{titlepage}
\centering
\vspace*{2cm}
{\Huge\bfseries Assignment 3\par}
\vspace{0.5cm}
{\Large Transaction Management, Recovery, and High-Concurrency Validation\par}
\vspace{1.5cm}
{\large\textbf{CS 432: Databases}\par}
{\large Semester II, 2025--2026\par}
\vspace{1cm}
{\large Indian Institute of Technology, Gandhinagar\par}
\vspace{2cm}

\begin{tabular}{lll}
\hline
\textbf{Team Members} & \textbf{Module} & \textbf{Role} \\
\hline
Parthiv Patel & A & Transaction engine + recovery integration \\
Laksh Jain & A & B+ tree DB internals + API integration \\
Shriniket Behera & A & Constraints + isolation + ACID validation \\
Ridham Patel & B & Stress harness design + reporting pipeline \\
Rudra Pratap Singh & B & Concurrency/race/failure test implementation \\
\hline
\end{tabular}

\vspace{1.5cm}
{\large\textbf{Repository:} \url{https://github.com/ridhamp4/Databases-Track-1-Assignment-3}\par}
\vspace{0.4cm}
{\large\textbf{Video Links:}\par}
{\large Module A (ACID over B+Tree): \href{https://drive.google.com/drive/folders/1mQhuZsHSjTK9E0fT-kfTcObeqIXp6DEE?usp=sharing}{Google Drive Link}\par}
{\large Module B (API/Application testing + Locust): \href{https://drive.google.com/drive/folders/1JIU-ww6tLI8o2geELsPQ9wfkWjCJDl0t?usp=sharing}{Google Drive Link}\par}
\vspace{0.8cm}
\begin{tabular}{ll}
\hline
\textbf{Module} & \textbf{Artifact} \\
\hline
Module A & \texttt{ModuleA/} implementation + ACID tests \\
Module B & \texttt{ModuleB/stress\_tests/module\_b\_stress.py} + \texttt{ModuleB/stress\_tests/locustfile.py} \\
\hline
\end{tabular}

\vfill
\begin{center}
\fbox{\parbox{0.9\textwidth}{\centering\small
\textbf{Primary Result File:} \texttt{ModuleB/stress\_tests/module\_b\_results.json} \\
\textbf{Tool-based stress:} Locust headless run (e.g., 100 users for 20 seconds)
}}
\end{center}
\vspace{1cm}
\end{titlepage}

\tableofcontents
\newpage

% #####################################################################
%                           VIDEO LINKS
% #####################################################################
\section*{Video Links}
\addcontentsline{toc}{section}{Video Links}

\begin{itemize}[noitemsep]
  \item \textbf{Module A (ACID over B+Tree):} \href{https://drive.google.com/drive/folders/1mQhuZsHSjTK9E0fT-kfTcObeqIXp6DEE?usp=sharing}{https://drive.google.com/drive/folders/1mQhuZsHSjTK9E0fT-kfTcObeqIXp6DEE}
  \item \textbf{Module B (API/Application testing + Locust):} \href{https://drive.google.com/drive/folders/1JIU-ww6tLI8o2geELsPQ9wfkWjCJDl0t?usp=sharing}{https://drive.google.com/drive/folders/1JIU-ww6tLI8o2geELsPQ9wfkWjCJDl0t}
\end{itemize}

% #####################################################################
%                        AIM / PRINCIPLE / PS
% #####################################################################
\section{Aim, Principle, and Problem Statement}

\subsection{Aim}
The objective is to make a B+ tree based mini database robust under both normal and high-contention workloads by combining reliable transaction semantics with stress validation.

\subsection{Principle}
The system is designed around ACID properties:
\begin{itemize}[noitemsep]
  \item \textbf{Atomicity}: all-or-nothing multi-step transactions.
  \item \textbf{Consistency}: constraints and invariants are preserved.
  \item \textbf{Isolation}: concurrent operations do not expose corrupted intermediate state.
  \item \textbf{Durability}: committed state survives restart via WAL replay.
\end{itemize}

\subsection{Problem Statement (PS)}
We must validate that a custom B+ tree database engine supports correct multi-relation transactional behavior, recovery after failure, and safe performance under heavy concurrent operations.

\begin{lstlisting}[style=python, caption={Minimal three-table transactional scenario targeted by Assignment 3}]
tx_id = dbm.begin()
users.update(user_id, updated_user, tx_id=tx_id)
products.update(product_id, updated_product, tx_id=tx_id)
orders.insert(new_order, tx_id=tx_id)
dbm.commit(tx_id)
\end{lstlisting}

% #####################################################################
%                        BROAD PLAN
% #####################################################################
\section{Broad Plan}

\begin{enumerate}[noitemsep]
  \item Strengthen Module A with transaction management, WAL-based recovery, constraints, and isolation mechanisms.
  \item Build Module B harnesses to generate concurrent workloads, race conditions, failure injection, and stress traffic.
  \item Evaluate with deterministic checks and summarize ACID outcomes from measured runs.
\end{enumerate}

\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Execution plan used in practice}]
# Module A validation
cd ModuleA
python test/Atomicity.py --mode crash
python test/Atomicity.py --mode verify

# Module B API-level stress (original)
cd ../ModuleB
python stress_tests/module_b_stress.py --base-url http://localhost:5001

# Module B tool-based stress (Locust)
locust -f stress_tests/locustfile.py --host http://localhost:5001 --headless \
  -u 100 -r 25 --run-time 20s --stop-timeout 5 --csv stress_tests/locust_module_b --only-summary
\end{lstlisting}

% #####################################################################
%                        MODULE A
% #####################################################################
\part*{Module A: Transaction Engine and Recovery over B+ Tree}
\addcontentsline{toc}{part}{Module A: Transaction Engine and Recovery over B+ Tree}

\section{Implementation Details (Module A)}

\subsection{Engine Architecture}
Each relation is stored as a dedicated B+ tree. All mutations occur directly on table B+ trees through table abstractions managed by \texttt{DatabaseManager}.

Core files:
\begin{itemize}[noitemsep]
  \item \texttt{ModuleA/database/bplustree.py}
  \item \texttt{ModuleA/database/table.py}
  \item \texttt{ModuleA/database/transaction.py}
  \item \texttt{ModuleA/database/db\_manager.py}
\end{itemize}

\subsection{Transaction and WAL Workflow}
\begin{enumerate}[noitemsep]
  \item \textbf{BEGIN}: create tx state, acquire isolation lock, append \texttt{TX\_START}.
  \item \textbf{DML}: log operation with old/new image before applying mutation.
  \item \textbf{COMMIT}: append \texttt{TX\_COMMIT} and release lock.
  \item \textbf{ROLLBACK}: undo ops in reverse order, append \texttt{TX\_ROLLBACK}.
\end{enumerate}

\begin{lstlisting}[style=python, caption={WAL logging in transaction manager (Module A)}]
def log_op(self, tx_id, op_type, db_name, table_name, key, old_value, new_value):
    tx = self.ensure_active(tx_id)
    entry = {
        "type": op_type,
        "tx_id": tx_id,
        "db": db_name,
        "table": table_name,
        "key": key,
        "old": old_value,
        "new": new_value,
    }
    self._append_log(entry)
    tx.ops.append(entry)
\end{lstlisting}

\subsection{Constraints and Consistency Guards}
Database-layer validation enforces:
\begin{itemize}[noitemsep]
  \item non-negative numeric fields (e.g., \texttt{balance}, \texttt{stock}, \texttt{amount}),
  \item primary key integrity,
  \item foreign-key-style reference checks across tables.
\end{itemize}

\subsection{Recovery Logic}
Restart recovery parses WAL and partitions transactions into \texttt{started}, \texttt{committed}, and \texttt{rolled\_back}. Recovery then applies:
\[
\text{incomplete} = \text{started} - \text{committed} - \text{rolled\_back}
\]
\begin{itemize}[noitemsep]
  \item REDO all committed operations in log order.
  \item UNDO only incomplete operations in reverse order.
\end{itemize}

\begin{lstlisting}[style=python, caption={Durability fix: UNDO only incomplete transactions}]
incomplete = started - committed - rolled_back
redo_ops = [op for op in ops if op.get("tx_id") in committed]
undo_ops = [
    op for op in reversed(ops)
    if op.get("tx_id") in incomplete
]
db_manager.apply_recovery_ops(redo_ops, undo_ops)
\end{lstlisting}

This avoids double-undo of already rolled-back transactions and was required to make durability pass under large rollback-heavy stress.

\section{Module A Results}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\hline
\textbf{Property} & \textbf{Result} \\
\hline
Atomicity & PASS (rollback after injected failure) \\
Consistency & PASS (constraint violations rejected) \\
Isolation & PASS (serializable behavior under shared data contention) \\
Durability & PASS (committed state preserved after restart) \\
Multi-relation transaction demo & PASS (Users, Products, Orders updated atomically) \\
\hline
\end{tabularx}
\caption{Module A validation summary}
\end{table}

\begin{lstlisting}[style=python, caption={Example ACID check output pattern from Module A tests}]
Atomicity: PASS
Consistency: PASS
Isolation: PASS
Durability: PASS
\end{lstlisting}

% #####################################################################
%                        MODULE B
% #####################################################################
\newpage
\part*{Module B: Concurrent Workload and Stress Testing (API/Application Perspective)}
\addcontentsline{toc}{part}{Module B: Concurrent Workload and Stress Testing (API/Application Perspective)}

\section{Implementation Details (Module B)}

\subsection{Assignment2 Flask Backend Stress (module\_b\_stress.py)}
The original Module B implementation directly stress-tests the Assignment2 Flask backend service (running at \texttt{http://localhost:5001}) and validates multi-user behavior at API level.

Primary script:
\begin{lstlisting}[basicstyle=\ttfamily\small]
ModuleB/stress_tests/module_b_stress.py
\end{lstlisting}

Backend run + stress run flow:
\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Original Module B backend stress execution flow}]
# Terminal 1: start Assignment2 Flask backend
cd ModuleB/Assignment2/app/backend
python app.py

# Terminal 2: run original Module B stress harness
cd ModuleB
python stress_tests/module_b_stress.py --base-url http://localhost:5001
\end{lstlisting}

Representative API areas covered by this original harness:
\begin{itemize}[noitemsep]
  \item auth login and token-based session flow,
  \item post creation, likes, comments,
  \item poll creation and concurrent voting,
  \item group join race probes,
  \item transaction failure simulation in backend DB path,
  \item read-heavy stress throughput and latency summary.
\end{itemize}

\subsubsection{Concurrent Usage (How we do it)}
We simulate many logged-in users performing writes at the same time. The harness first creates a \emph{shared post}, \emph{shared poll}, and \emph{shared group}, then runs concurrent requests from multiple user sessions against these shared resources.

Concretely, the harness:
\begin{itemize}[noitemsep]
  \item creates multiple authenticated sessions via \texttt{/api/auth/login},
  \item issues concurrent \texttt{POST} requests for likes/comments/votes/joins, targeting the same artifact IDs,
  \item verifies users do not interfere using database checks and expected count ranges written to \texttt{module\_b\_results.json}.
\end{itemize}

Representative workload pattern from the original harness:
\begin{lstlisting}[style=python, caption={Concurrent API writes in module\_b\_stress.py (representative)}]
with ThreadPoolExecutor(max_workers=concurrency) as executor:
  like_results = list(executor.map(
    lambda session: http_json_request_with_retry(
      base_url,
      "POST",
      f"/api/posts/{shared['post_id']}/like",
      None,
      session.token,
    ),
    like_inputs,
  ))
\end{lstlisting}

\textbf{How we tested it (verification + pass criteria).}
We run the harness with a concurrency-heavy configuration and verify both the printed summary and the stored JSON report.

\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Concurrent-usage test run command (Module B)}]
# Terminal 1: start backend
cd ModuleB/Assignment2/app/backend
python app.py

# Terminal 2: run harness
cd ModuleB
python stress_tests/module_b_stress.py \
  --base-url http://localhost:5001 \
  --concurrent-ops 1000 \
  --concurrent-concurrency 128
\end{lstlisting}

On-screen verification during evaluation:
\begin{itemize}[noitemsep]
  \item show the terminal summary printed by the harness (Concurrent Usage: PASS/FAIL),
  \item open \texttt{ModuleB/stress\_tests/module\_b\_results.json} and check:
    \begin{itemize}[noitemsep]
      \item \texttt{concurrentUsage.db\_counts} vs \texttt{concurrentUsage.expected},
      \item \texttt{verdict.concurrent\_usage\_ok == true}.
    \end{itemize}
\end{itemize}

\subsubsection{Race Condition Testing (How we do it)}
We pick critical operations where races commonly create duplicates or inconsistent state, and we run many concurrent attempts against the \emph{same} record.

Critical operations selected in this application:
\begin{itemize}[noitemsep]
  \item liking the same post (should be at most 1 like per user per post),
  \item voting on the same poll (exactly 1 vote per user for a poll),
  \item joining the same group (exactly 1 membership row per user per group).
\end{itemize}

The harness executes repeated concurrent attempts, then checks the database for duplicates. Example DB checks (stored in \texttt{raceConditionProbes.db\_checks} in the JSON):
\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Representative race-condition DB checks (no duplicates)}]
SELECT COUNT(*)
FROM PostLike
WHERE PostID = <shared_post_id> AND MemberID = <actor_id>;

SELECT COUNT(*)
FROM PollVote pv
JOIN PollOption po ON pv.OptionID = po.OptionID
WHERE po.PollID = <poll_id> AND pv.MemberID = <actor_id>;

SELECT COUNT(*)
FROM GroupMembership
WHERE GroupID = <group_id> AND MemberID = <actor_id>;
\end{lstlisting}

Pass condition: these counts match the expected bounds (e.g., 0--1 for post-like rows, exactly 1 for vote and membership).

\textbf{How we tested it (verification + pass criteria).}
We run the harness with a high number of attempts and high worker concurrency for the race probes, then verify that DB counts match expected constraints.

\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Race-condition test run command (Module B)}]
cd ModuleB
python stress_tests/module_b_stress.py \
  --base-url http://localhost:5001 \
  --race-attempts 1000 \
  --race-concurrency 128
\end{lstlisting}

Pass criteria in the JSON report:
\begin{itemize}[noitemsep]
  \item \texttt{raceConditionProbes.db\_checks} matches \texttt{raceConditionProbes.expected},
  \item \texttt{verdict.race\_conditions\_ok == true}.
\end{itemize}

\subsubsection{Failure Simulation (How we do it)}
We introduce a deliberate database failure \emph{mid-transaction} to ensure the system rolls back correctly and does not persist partial data.

Implementation idea:
\begin{itemize}[noitemsep]
  \item execute a valid insert (e.g., insert a new post row),
  \item immediately execute an invalid SQL statement (insert into a missing table) to force an exception,
  \item call \texttt{rollback()},
  \item verify that no marker rows exist in the database.
\end{itemize}

Representative code from the harness:
\begin{lstlisting}[style=python, caption={Failure simulation + rollback verification in module\_b\_stress.py (representative)}]
cursor.execute(
  "INSERT INTO Post (AuthorID, GroupID, Content, ImageURL, CreatedAt) VALUES (%s,%s,%s,%s,NOW())",
  (creator.member_id, None, marker, None),
)
cursor.execute("INSERT INTO DefinitelyMissingTable (x) VALUES (1)")
conn.commit()

... except Exception:
  conn.rollback()

remaining = db_fetch_one(
  "SELECT COUNT(*) AS c FROM Post WHERE Content LIKE %s",
  (f"{marker_prefix}%",),
)
\end{lstlisting}

\textbf{How we tested it (verification + pass criteria).}
We run many iterations of the forced-failure transaction and verify that every iteration fails and leaves no persisted marker rows.

\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Failure-simulation test run command (Module B)}]
cd ModuleB
python stress_tests/module_b_stress.py \
  --base-url http://localhost:5001 \
  --failure-iterations 1000
\end{lstlisting}

Pass criteria in \texttt{ModuleB/stress\_tests/module\_b\_results.json}:
\begin{itemize}[noitemsep]
  \item \texttt{failureSimulation.forced\_errors\_seen == failureSimulation.iterations},
  \item \texttt{failureSimulation.unexpected\_successes == 0},
  \item \texttt{failureSimulation.rolled\_back\_row\_count == 0},
  \item \texttt{verdict.rollback\_ok == true}.
\end{itemize}

\subsubsection{Stress Testing (How we do it)}
We run a large number of requests (hundreds or thousands) and observe behaviour under load:
\begin{itemize}[noitemsep]
  \item correctness: requests succeed (HTTP 200) and the earlier concurrent/race/failure checks still pass,
  \item performance: we compute response-time percentiles (P50/P95) and average latency.
\end{itemize}

Our implementation supports two stress approaches:
\begin{enumerate}[noitemsep]
  \item \textbf{Built-in harness stress phase}: multi-threaded \texttt{GET} traffic to \texttt{/api/posts}, \texttt{/api/groups/}, \texttt{/api/polls/} and percentile timing summary in \texttt{module\_b\_results.json}.
  \item \textbf{Tool-based stress (Locust)}: headless Locust run against the backend (CSV + summary).
\end{enumerate}

\textbf{How we tested it (verification + pass criteria).}

Built-in harness stress phase:
\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Built-in stress test run command (Module B)}]
cd ModuleB
python stress_tests/module_b_stress.py \
  --base-url http://localhost:5001 \
  --stress-requests 2000 \
  --stress-concurrency 64
\end{lstlisting}

Verification:
\begin{itemize}[noitemsep]
  \item open \texttt{module\_b\_results.json} and check \texttt{stressTest.status\_counts} contains only HTTP 200 responses,
  \item report \texttt{stressTest.timings\_ms.p50} and \texttt{stressTest.timings\_ms.p95} as the response-time summary,
  \item confirm \texttt{verdict.stress\_ok == true}.
\end{itemize}

Original reported outcomes (from Module B README):
\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\hline
\textbf{Test Area} & \textbf{Observed Result} \\
\hline
Concurrent Usage & PASS \\
Race Condition Testing & PASS \\
Failure Simulation & PASS \\
Stress Testing & PASS \\
Locust Run (100 users, 20s) & 2734 requests, 0 failures, avg 386 ms, P95 750 ms \\
\hline
\end{tabularx}
\caption{Module B API/application testing summary}
\end{table}

Measured snapshot from \texttt{module\_b\_results.json} (Assignment2 backend run):
\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\hline
\textbf{Metric from Original Harness Output} & \textbf{Observed Value} \\
\hline
Concurrent usage comments (DB count) & 1000 \\
Concurrent usage votes (DB count) & 6 \\
Failure simulation forced errors seen & 1000 \\
Failure simulation rollback row count & 0 (rollback successful) \\
Stress test requests & 1000 \\
Stress test average latency & 512.09 ms \\
Stress test P95 latency & 1496.53 ms \\
\hline
\end{tabularx}
\caption{Concrete values from \texttt{ModuleB/stress\_tests/module\_b\_results.json}}
\end{table}

\subsection{Tool-Based Stress Testing (Locust)}
To satisfy the tool-based stress requirement, we used Locust against the same Assignment2 backend.

\begin{lstlisting}[basicstyle=\ttfamily\small, caption={Locust command used for Module B stress testing}]
cd ModuleB
locust -f stress_tests/locustfile.py --host http://localhost:5001 --headless \
  -u 100 -r 25 --run-time 20s --stop-timeout 5 --csv stress_tests/locust_module_b --only-summary
\end{lstlisting}

The Locust outputs include a console summary and CSV artifacts under \texttt{ModuleB/stress\_tests/} (e.g., \texttt{locust\_module\_b\_stats.csv}).

% #####################################################################
%                        INTERPRETATION
% #####################################################################
\section{Result Interpretation}

\subsection{Module A Interpretation}
The WAL old/new image model with ordered redo and reverse undo gives deterministic state reconstruction. The corrected incomplete-transaction filter improves durability reliability when workloads have frequent rollback events.

\begin{lstlisting}[style=python, caption={Interpretation anchor: recovery partitioning logic}]
incomplete = started - committed - rolled_back
# only incomplete txns are undone during restart
\end{lstlisting}

\subsection{Module B Interpretation}
The API-level tests demonstrate multi-user correctness: concurrent requests do not create duplicate likes/votes/joins, and deliberate SQL failures do not leave partial rows due to rollback. Locust validates robustness under sustained concurrent read-heavy load.

\begin{lstlisting}[style=python, caption={Interpretation anchor: rollback verification in module\_b\_stress.py}]
rollback_ok = (
  failure_simulation["rolled_back_row_count"] == 0
  and failure_simulation["forced_errors_seen"] == failure_simulation["iterations"]
  and failure_simulation["unexpected_successes"] == 0
)
\end{lstlisting}

\subsection{End-to-End Interpretation}
Together, Module A and Module B demonstrate a robust pipeline: transactional correctness at B+Tree engine level and behaviorally safe execution under concurrent API workloads for the Assignment2 application.

% #####################################################################
%                        REPRODUCIBILITY
% #####################################################################
\section{Reproducibility}

\begin{lstlisting}[basicstyle=\ttfamily\small]
cd ModuleB/Assignment2/app/backend
python app.py

cd ../../../
python ModuleB/stress_tests/module_b_stress.py --base-url http://localhost:5001

cd ModuleB
locust -f stress_tests/locustfile.py --host http://localhost:5001 --headless \
  -u 100 -r 25 --run-time 20s --stop-timeout 5 --csv stress_tests/locust_module_b --only-summary
\end{lstlisting}

Primary output file:
\begin{itemize}[noitemsep]
  \item \texttt{ModuleB/stress\_tests/module\_b\_results.json}
  \item Locust CSV outputs in \texttt{ModuleB/stress\_tests/} (e.g., \texttt{locust\_module\_b\_stats.csv})
\end{itemize}

% #####################################################################
%                        TEAM CONTRIBUTIONS
% #####################################################################
\section*{Team Member Contributions}
\addcontentsline{toc}{section}{Team Member Contributions}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\hline
\textbf{Member} & \textbf{Contributions} \\
\hline
Parthiv Patel & Module A: transaction workflow integration, route-level transaction APIs, and ACID validation support \\
Laksh Jain & Module A: B+ tree database internals, table/database abstractions, and recovery integration \\
Shriniket Behera & Module A: consistency constraints, isolation controls, and durability/recovery fixes \\
Ridham Patel & Module B: stress harness orchestration, report generation pipeline, and run automation \\
Rudra Pratap Singh & Module B: concurrent usage, race probes, failure simulation verification, and stress-test execution support \\
\hline
\end{tabularx}
\end{table}

\end{document}
